% Matt Adelman's Resume
% Written in LaTeX for clarity and a challenge.
\documentclass[11pt]{res} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font
%(download helvetica.sty)
%\usepackage{newcent}
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\newsectionwidth{0pt}  % So the text is not indented under section headings

% For margins to be how I like them.
\usepackage[margin=0.5in, paperwidth=8.5in, paperheight=11in]{geometry}

\begin{document}


% I didn't like my name being in the center, so I changed the default.
{\bf\Large Matthew Adelman}

\address{2394 Williams Street $\bullet$ Palo Alto, CA 94306 \\
        (201) 323-2719 $\bullet$ mxadelman@gmail.com}

% Second address area to make the first one flush left
\address{}

\begin{resume}

\section{Computer Skills}
GitHub: https://github.com/adelman\\
Programming Languages: Java, SQL, Ruby, Python, SML, JavaScript.\\
Considerable Experience: Unix, Git, AWS, Ruby on Rails, Pega, \LaTeX, GnuPlot,
Mathematica, Photoshop.\\
Basic Experience: HTML5, CSS3, jQuery

\section{EXPERIENCE}
{\bf Fiksu DSP}, Boston, MA\\
{\it Team Lead} \hfill June 2015 - June 2017 \\
{\it Software Engineer} \hfill February 2014 - June 2015\!

\vspace{0.01in} % Make a bit of space before the items.
   \begin{itemize} \itemsep -2pt  % reduce space between items
   \item Managed team of five engineers in the development of a completely new
     client facing user interface.
   \item Received significant positive feedback from team members, compared to
     their experience working for others.
   \item Maintained multiple Amazon Redshift clusters, responsible for ingesting
     over 100 million events each day.
   \item Expanded the real-time bidding system to process over one million
     events per second, by integrating new exchanges and easing the construction
     of new campaigns.
   \item Built audience-processing infrastructure which
     currently evaluates over three billion user profiles each hour.
   \item Streamlined lookalike-processing for audiences.
   \item Tuned bid-adjustment and budget-allocation systems for
     optimization team to bid more precisely.
   \item Led the implementation of a new Aerospike Cluster, saving over
     \$200,000 annually.
   \item Additional \$10,000 saved per month through AWS cost cutting measures.
   \end{itemize}

% How to say different positions
% How to say different companies?
% What can I say about big data, ingestion, moving to a different system


{\bf Accenture}, Beverly, MA \hfill June 2013 - January 2014 \\
{\it Software Engineer}
\vspace{0.01in} % Make a bit of space before the items.
   \begin{itemize} \itemsep -2pt  % reduce space between items
   \item Worked with the Pega Business Process Management framework to develop
   large scale enterprise solutions,
   specifically user interfaces.
   \item Built solutions for clients ranging in size from small start-ups to the
     FBI and USDA.
   \item Balanced the every day needs of consultants with the overall needs
     of clients to move projects forward at the appropriate pace.
   \end{itemize}


{\bf Wesleyan University Math / Computer Science Department}, Middletown, CT
\hfill Fall 2011 - May 2013 \\
{\it Course Assistant and Tutor} \\
\vspace{-0.17in}
 \begin{itemize} \itemsep -2pt
   \item Hold bi-weekly tutoring sessions and grade problem sets for Computer
   Science 1, Algorithms and Complexity, and Functional Data Structures.
   \end{itemize}

\vspace{-0.05in} % Bring the sections closer together.



%section{CAMPUS ACTIVITIES}
%\bf Alpha Delta Phi Society} Middletown, CT \hfill Fall 2009 - Present\\
%\it Steward} \hfill Spring 2011 - Fall 2011\\
%vspace{-0.17in}
%\begin{itemize} \itemsep -2pt
%  \item Managed the Star \& Crescent restaurant, a popular dining location on
%  campus.
%  \item Oversaw payroll of 13 kitchen employees, including one professional
%  chef.
%  \item Maintained favorable supplier relationship for beneficial pricing
%  terms.
%  \item Listened to student demand to create desirable menus.
%  \end{itemize}

%vspace{-0.1in}
%
%\it President } \hfill Fall 2012\\
%vspace{-0.17in}
%\begin{itemize} \itemsep -2pt
%  \item Facilitated weekly meetings among executive committee officers.
%  \item Compiled a bi-semesterly ``State of Society'' report for our Board of
%  Trustees.
%  \item Fostered positive relations between the Society, the University, and
%  the greater Middletown Community.
%  \end{itemize}

%vspace{-0.1in}
%
%\it Critic } \hfill Spring 2012\\
%vspace{-0.17in}
%\begin{itemize} \itemsep -2pt
%  \item Responsible for the emotional well-being of all members.
%  \item Mediating difficult discussions between members.
%  \item Held pledge education sessions for the semesters' pledge class.
%  \item Organized all pledge related events, including initiation.
%  \end{itemize}

\section{EDUCATION}
 \noindent Wesleyan University, Middletown, CT \\
{\it Bachelor of Arts}, May 2013 \\
Majors: Computer Science and Mathematics, GPA: 3.60/4.00 \\
{\bf Relevant Coursework:} Advanced Functional Data Structures, Advanced and
Experimental Algorithmics, Graduate Algebra, Algebraic Geometry, Mathematical
Logic, and Design of Programming Languages


\section{Interests}
Photography, SCUBA Diving, Travel, Fire Arts, Rubik's Cubes and other twisty
puzzles, Robotics, and Taiko

\end{resume}

\end{document}
